---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# cactusapi <img src="man/figures/logo.svg" align="right" height="139" />

<!-- badges: start -->
[![R-CMD-check](https://github.com/RaoulWolf/cactusapi/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/RaoulWolf/cactusapi/actions/workflows/R-CMD-check.yaml)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![Codecov test coverage](https://codecov.io/gh/RaoulWolf/cactusapi/branch/master/graph/badge.svg)](https://app.codecov.io/gh/RaoulWolf/cactusapi?branch=master)
<!-- badges: end -->

> A [ZeroPM](https://zeropm.eu/) R package

The goal of the cactusapi package is to provide a minimal and lightweight 
interface to the 
[CACTUS Chemical Identifier Resolver](https://cactus.nci.nih.gov/chemical/structure) 
API services. 

The dependency of cactusapi is kept at a bare minimum: 
[curl](https://cran.r-project.org/web/packages/curl/index.html) for handling 
the API requests.

## Installation

You can install the development version of cccapi from 
[GitHub](https://github.com/) with:

``` {r install}
#| eval = FALSE
# install.packages(devtools)
remotes::install_github("RaoulWolf/cactusapi")
```

## Example

This is a basic example which shows you how to get the InChI representation of 
caffeine:

```{r example}
library(cactusapi)

get_representation(
  structure_identifier = "caffeine", 
  representation = "StdInChI"
)
```

## Acknowledgement

This R package was developed by the EnviData initiative at the 
[Norwegian Geotechnical Institute (NGI)](https://www.ngi.no/eng) as part of the 
project 
[ZeroPM: Zero pollution of Persistent, Mobile substances](https://zeropm.eu/). 
This project has received funding from the European Union's Horizon 2020 
research and innovation programme under grant agreement No 101036756.

---

If you find this package useful and can afford it, please consider making a 
donation to a humanitarian non-profit organization, such as 
[Sea-Watch](https://sea-watch.org/en/). Thank you. 
